Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-22 Master Thesis/synopsis.tex
Mention Néron-Severi group

\begin{proof}
We have the following exact sequence:
\[ 0\longrightarrow \operatorname{Pic}^0(C) \longrightarrow\operatorname{Pic}(C) \longrightarrow \mathbb{Z} \longrightarrow 0  \]
Now $\operatorname{Pic}^0(C)$ can be identified with the $F$-rational points of the Jacobian variety $J$ of $C$. $J(F)$ is finitely generated by the Mordell-Weil Theorem \ref{mordell-weil-theorem}, hence $\operatorname{Pic}(C)$ is finitely generated as well.
\end{proof}

>>>>

\begin{proof}
We have the following exact sequence:
\[ 0\longrightarrow \operatorname{Pic}^0(C) \longrightarrow\operatorname{Pic}(C) \longrightarrow \operatorname{NS}(C) \longrightarrow 0  \]
where $\operatorname{NS}(C)$ denotes the finitely generated Néron-Severi group of $C$. Now $\operatorname{Pic}^0(C)$ can be identified with the $F$-rational points of the Jacobian variety $J$ of $C$. $J(F)$ is finitely generated by the Mordell-Weil Theorem \ref{mordell-weil-theorem}, hence $\operatorname{Pic}(C)$ is finitely generated as well.
\end{proof}
